Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Thresholds

\begin{itemize}
  \item \textbf{Referenced Types:} For all types references in the code, we should compare their FQI with other code fragements to ensure functional equality.
  \item \textbf{Variables:} We trace the declaration of used variables to ensure that their type equals the type of another equally named variable.
  \item \textbf{Method Calls:} A codebase can have several methods with equal names, but a different implementation. Because of this, we compare the FQI of the method signature of called methods. A method signature includes the FQI for a methods' name, return value and each of its arguments.
\end{itemize}

@@

CloneRefactor walks the AST and collects each declaration and statement. It then builds a graph representation on basis of this AST, in which each declaration and statement becomes a node. This graph representation maps the following relations for each declaration and statement:

@@

\subsection{Thresholds}\label{chap:thresholds}

>>>>

\begin{itemize}
  \item \textbf{Referenced Types:} For all types references in the code, we should compare their FQI with other code fragments to ensure functional equality.
  \item \textbf{Variables:} We trace the declaration of used variables to ensure that their type equals the type of another equally named variable.
  \item \textbf{Method Calls:} A codebase can have several methods with equal names, but a different implementation. Because of this, we compare the FQI of the method signature of called methods. A method signature includes the FQI for a methods' name, return value and each of its arguments.
\end{itemize}

@@

CloneRefactor walks the AST and collects each declaration and statement (similar to the Scorpio clone detection tool \cite{higo2013revisiting}). It then builds a graph representation on basis of this AST, in which each declaration and statement becomes a node. This graph representation maps the following relations for each declaration and statement:

@@

\subsection{Thresholds}\label{chap:thresholds}
Thresholds are a tool that aid in the process of deciding whether a clone \textit{should} be refactored. Many clone detection tools focus on either the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, number of tokens \cite{roy2008nicad, sajnani2016sourcerercc, ragkhitwetsagul2019siamese} and/or number of nodes (declarations/statements) \cite{higo2013revisiting} to decide whether code fragments should be considered clones of each other. A comparison of clone detection tools by Bellon et al. \cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone. The Scorpio clone detection tool uses this same number as minimum number of nodes \cite{higo2013revisiting}. Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone.

However, we would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored. For instance
